---
title: "Using Git & GitHub with R"
author: "David Keyes"
date: July 2, 2024
format:
  html:
    code-link: true
    code-fold: true
    self-contained: true
    embed-resources: true
    toc: true
    theme: Zephyr
    number-sections: false
execute: 
  warning: false
  message: false
  echo: false
editor_options: 
  chunk_output_type: console
---

# Using Git and GitHub with R

```{r libraries}
#| echo: true

library(tidyverse)
library(usethis)

```

## Create a local Git Repository

This lesson displays how to load and use the package `usethis` to create. And next type \`use_git() to create a git repository for an initial commit.

`use_git()` gives several options to commit for using Git and GitHub with R.Rproj. Then it asks to activate the Git pane, which requires to restart.

```{r git_repository}
#|echo: true

library(usethis)

# use_git()

```

### Commits

They are snapshots of the code. It keeps track of the history of the coding process.

Commits have two parts.

1.  Staging a file

2.  Draft a `commit message` with keywords describing the content at the moment of the snapshot was created.

## Commit history

In the Environment panel under Git tab there is a sub-tab title History.It keeps records of the changes done to the Readme.md file.

## GitHub repositories
